### 2021-03-12 2021.csic5011/homework/homework05.tex
Add files via upload

\lecture{Homework 5. SDP Extensions of PCA and MDS}{Yuan Yao}{Due: 1.5 weeks}{Mar. 18, 2020}

@@

\begin{enumerate}
\item Set $m=n=20$, $r=1$, and $p=0.1$, use Matlab toolbox CVX to formulate a semi-definite program for Robust PCA of $M$:
\begin{eqnarray} \label{eq:RPCA_SDP}
& \min & \frac{1}{2} (\tr(W_1)+\tr(W_2)) + \lambda \|S\|_1 \\
& s.t. & L_{ij} +S_{ij} = X_{ij}, \quad (i,j)\in E  \nonumber \\
& & \displaystyle \left[ \begin{array}{cc} 
W_1 & L \\
L^T & W_2
\end{array}
\right] \succeq 0, \nonumber
\end{eqnarray}
where you can use the matlab implementation in lecture notes as a reference;
\item Choose different parameters $p\in [0,1]$ to explore the probability of successful recover;
\item Increase $r$ to explore the probability of successful recover;
\item $^\star$ Increase $m$ and $n$ to values beyond $50$ will make CVX difficult to solve. In this case, use the Augmented Lagrange Multiplier method, e.g. in E. J. Candes, X. Li, Y. Ma, and J. Wright (2009) "Robust Principal Component Analysis?". Journal of ACM, 58(1), 1-37. Make a code yourself (just a few lines of Matlab or Python) and test it for $m=n=1000$. A convergence criterion often used can be $\|M-\hat{L} - \hat{S} \|_F / \|M\|_F \leq \epsilon$ ($\epsilon=10^{-6}$ for example).  
\end{enumerate}

@@

\item{\em Protein Folding:} Consider the 3D structure reconstruction based on incomplete MDS with uncertainty. Data file:

>>>>

\lecture{Homework 5. SDP Extensions of PCA and MDS}{Yuan Yao}{Due: 1 week}{Mar. 12, 2021}

@@

\begin{enumerate}
\item Set $m=n=20$, $r=1$, and $p=0.1$, use Matlab toolbox CVX to formulate a semi-definite program for Robust PCA of $M$:
\begin{eqnarray} \label{eq:RPCA_SDP}
& \min & \frac{1}{2} (\tr(W_1)+\tr(W_2)) + \lambda \|S\|_1 \\
& s.t. & L_{ij} +S_{ij} = X_{ij}, \quad (i,j)\in E  \nonumber \\
& & \displaystyle \left[ \begin{array}{cc} 
W_1 & L \\
L^T & W_2
\end{array}
\right] \succeq 0, \nonumber
\end{eqnarray}
where you can use the matlab implementation in lecture notes as a reference;
\item Choose different parameters $p\in [0,1]$ to explore the probability of successful recover;
\item Increase $r$ to explore the probability of successful recover;
\item $^\star$ Increase $m$ and $n$ to values beyond $50$ will make CVX difficult to solve. In this case, use the Augmented Lagrange Multiplier method, e.g. in E. J. Candes, X. Li, Y. Ma, and J. Wright (2009) ``Robust Principal Component Analysis?". Journal of ACM, 58(1), 1-37. Make a code yourself (just a few lines of Matlab or Python) and test it for $m=n=1000$. A convergence criterion often used can be $\|M-\hat{L} - \hat{S} \|_F / \|M\|_F \leq \epsilon$ ($\epsilon=10^{-6}$ for example).  
\end{enumerate}

@@

\item{\em $^\star$Protein Folding:} Consider the 3D structure reconstruction based on incomplete MDS with uncertainty. Data file:
